**(a)**

```{r}
set.seed(1)
p=20
n=1000
x = matrix(rnorm(n*p),n,p)
B= rnorm(p)
B[3] = 0
B[5] = 0
B[6] = 0
B[10] = 0
B[18] = 0
eps = rnorm(n)
y = x%*%B + eps
```

**(b)**
```{r}
train = sample(1:dim(x)[1],100)
x.train = x[train,]
y.train = y[train,]
x.test = x[-train,]
y.test = y[-train,]
```

**(c)**
```{r}
library(leaps)
regfit.full = regsubsets(y ~ . , data = data.frame(x=x.train, y=y.train), nvmax=p)
summary(regfit.full)
```

Now, we will make predictions on training set.

```{r}
val.errors=rep(NA,20)
train.mat = model.matrix(y~.,data=data.frame(x=x.train,y=y.train))
for(i in 1:20){
  coefi = coef(regfit.full, id = i)
  pred = train.mat[,names(coefi)]%*%coefi
  val.errors[i] = mean((y.train-pred)^2)
}
```
plotting the training error:

```{r}
plot(val.errors, xlab="No. of predictors", ylab="Training MSE", type="b", pch=19)
```

**(d)**

```{r}
x_cols = colnames(x, do.NULL=F, prefix = "x.")
x_cols
```

```{r}
test.mat = model.matrix(y~., data = data.frame(x=x.test, y=y.test))
val.errorstest = rep(NA,20)
```


```{r}
for(i in 1:20){
  coefi = coef(regfit.full, id=i)
  pred = as.matrix(x.test[, x_cols %in% names(coefi)]) %*% coefi[names(coefi) %in% 
        x_cols]
  val.errorstest[i] = mean((y.test-pred)^2)
}
```

```{r}
plot(val.errorstest, type="b",pch=19)
```


**(e)**
test error is minimum for which size.

```{r}
which.min(val.errorstest)
```

**(f)**
```{r}
coef.best = coef(regfit.full, id=19)
coef.best
```

comparing coefficients:

```{r}
names(B) = paste0("x.",1:20)
merge(data.frame(beta=names(B),B),data.frame(beta=names(coef.best),coef.best),all.x=T, sort=F)
```


**(g)**
we will find error between estimated nad true coefficients.


```{r}
val.errors = rep(NA,20)
a = rep(NA,20)
b = rep(NA,20)
for (i in 1:20){
  coefi = coef(regfit.full, id=i)
  a[i] = length(coefi)-1
  b[i] = sqrt(sum((B[x_cols %in% names(coefi)] - coefi[names(coefi) %in% x_cols])^2) + 
  sum(B[!(x_cols %in% names(coefi))])^2)
}
```
plotting the errors:

```{r}
plot(x=a, y=b, xlab="Number of coefficients", ylab="error between estimated and true coefficients")

```
```{r}
which.min(b)
```
model with `r which.min(b)` coefficients minimizes the error between estimated and true coefficients, while test error is minimized with `r which.min(val.errorstest)`.