**Question No.-7**

We will try with no. of trees from 1 to 500 and m= $p$, $\frac{p}{2}$, $\sqrt{p}$.

we will make training set and test set to calculate errors:

```{r}
library(ISLR)
library(MASS)
library(randomForest)
attach(Boston)
```

```{r}
dim(Boston)
```

Now we will be using 300 observations as training data set and others as test data set.

```{r}
train = sample(1:nrow(Boston), 300)
boston.test = Boston[-train,]
```

No we will define different P,
```{r}
p = dim(Boston)[2]-1
p.2 = p/2
p.sq = sqrt(p)
```

Now, for getting error for every tree, we need to write loop:

```{r}

mse.p = rep(NA,50)
mse.p2 = rep(NA,50)
mse.psq = rep(NA,50)
  for( k in seq(1,500,10)){
    rf = randomForest(medv~., data= Boston, mtry=p, ntree=k)
    pred = predict(rf, newdata = Boston[-train,])
    mse.p[k] = mean((boston.test$medv - pred)^2)
  }

for( k in seq(1,500,10)){
    rf = randomForest(medv~., data= Boston, mtry=p.2, ntree=k)
    pred = predict(rf, newdata = Boston[-train,])
    mse.p2[k] = mean((boston.test$medv - pred)^2)
}

for( k in seq(1,500,10)){
    rf = randomForest(medv~., data= Boston, mtry=p.sq, ntree=k)
    pred = predict(rf, newdata = Boston[-train,])
    mse.psq[k] = mean((boston.test$medv - pred)^2)
}


```


Now we will plot the errors:
```{r}
plot(1:50, mse.p, col="blue", type="l", ylab ="TEST MSE", xlab = "No. of Trees")
lines(1:50,mse.p2, col="red", type="l")
lines(1:50,mse.psq, col="green", type="l")
legend("topright", legend = c("p","p.2","p.sq"), col=c("blue", "red","green"), lty = 1)

```
we can see that model with p/2 variables is giving lowest error.
